Model Samples Processing

### 2020-02-13 stats/model_sample_processing.Rmd
fb model run

model <- bind_rows(
 fread("../webppl/output/samples-fullyBayesian-pragmatic-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain1.csv",header = T)%>%mutate(chain = 1),
 fread("../webppl/output/samples-fullyBayesian-pragmatic-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain2.csv",header = T)%>%mutate(chain = 2),
 read("../webppl/output/samples-fullyBayesian-pragmatic-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain3.csv",header = T)%>%mutate(chain = 3),
  fread("../webppl/output/samples-fullyBayesian-pragmatic-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain4.csv",header = T)%>%mutate(chain = 4),
  fread("../webppl/output/samples-fullyBayesian-pragmatic-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain5.csv",header = T)%>%mutate(chain = 5),
  fread("../webppl/output/samples-fullyBayesian-pragmatic-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain6.csv",header = T)%>%mutate(chain = 6)
)

>>>>

model <- bind_rows(
 fread("../webppl/output/samples-fullyBayesian-pragmatic-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain1.csv",header = T)%>%mutate(chain = 1),
 fread("../webppl/output/samples-fullyBayesian-pragmatic-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain2.csv",header = T)%>%mutate(chain = 2),
 fread("../webppl/output/samples-fullyBayesian-pragmatic-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain3.csv",header = T)%>%mutate(chain = 3),
  fread("../webppl/output/samples-fullyBayesian-pragmatic-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain4.csv",header = T)%>%mutate(chain = 4),
  fread("../webppl/output/samples-fullyBayesian-pragmatic-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain5.csv",header = T)%>%mutate(chain = 5),
  fread("../webppl/output/samples-fullyBayesian-pragmatic-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain6.csv",header = T)%>%mutate(chain = 6)
)
